Graphical tests for coverage [@sailynoja2021graphical]

### 2021-11-30 docs/30-11-21_coverage/coverage.Rmd
Slides up for lab meeting

## Caliration

@@

I think people often talk about them as if they are interchangeable, which is probably fine.

@@

It would be good if 90% of the time the actual number was contained within that interval!

@@

**Note** this means we also want it to be outside the interval 10% of the time.
Saying you're 90% sure and being right 100% of the time (under-confidence) is also an error.

@@

It would be nice is there was some type of decomposition along the lines of
$$
\text{score(forecast)} = \text{calibration(forecast)} + \text{sharpness(forecast)},
$$
but AFAIK that doesn't exist.

@@

Given a collection of posterior predictive quantile results $q_1, \ldots, q_n$, what can we do?

**Main point** if our forecast is calibrated then $q_i \sim \mathcal{U}[0, 1]$.

@@

@@

@@

>>>>

## Calibration

@@

I think people often talk about them as if they are interchangeable, which is probably fine.
The difference is mostly about philosophical interpretation, and I'd guess most people talking about confidence intervals have the credible interval interpretation in mind.

@@

It would be good if 90% of the time the actual number was contained within that interval! Then we can say that our app is **calibrated**.

@@

**Note** this means we also want it to be outside the interval 10% of the time.
Saying you're 90% sure and being right 100% of the time is also an error.

It helps to have sample size.
For small sample size then if you're 90% sure then you'd hope you're right.

@@

## Decomposition of SPSR

It would be nice is there was some type of decomposition along the lines of
$$
\text{score(forecast)} = \text{calibration(forecast)} + \text{sharpness(forecast)},
$$
Wikipedia says that:

> The expectation value of a proper scoring rule can be decomposed into the sum of three components, called uncertainty, reliability, and resolution.

@@

Collection of posterior predictive quantile results $q_1, \ldots, q_n$, then what can we do?

**Main point** if our forecast is calibrated then $q_i \sim \mathcal{U}[0, 1]$ because the truth is a draw from the posterior predictive.
Sometimes called "Probability Integral Transform".

@@

## BP (before paper)

@@

1. **PIT-histograms** True value should lie in each decile 10% of the time so that the grey bars are level with the blue dashed line.
2. **Nominal coverage versus actual coverage** If nominal coverage equals actual coverage then the grey line should be along the green line.

@@

## AP (after paper)

* That second plot is alright, but how far can we reasonably expect the empirical coverage to stray from the nominal coverage? Especially when we are considerince all the possible confidence levels $\alpha$ simultaneously
* One answer provided by @sailynoja2021graphical who give "simultaneous confidence bands" which "jointly satisfy a desired coverage"
* Code is available: github.com/TeemuSailynoja/simultaneous-confidence-bands

```{r}
knitr::include_graphics("twitter_new1.png")
```

```{r}
knitr::include_graphics("twitter_new2.png")
```
